Supplemental Appendix for ``An asymptotically normal out-of-sample test of equal predictive accuracy for nested models''

### 2014-10-29 appendix.tex
Update homepage listed on paper and appendix

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft \protect\url{http://gray.clhn.co}\guillemotright.}\\%
  Iowa State University}

>>>>

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.}\\%
  Iowa State University}
